Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-27 Thesis/chapter/01-introduction.tex
formatting

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Gls{pv} is one viable option when becoming carbon neutral. 
Furthermore, 
it uses the suns energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of \gls{pv} are \gls{cigs}\cite{Vasekar2010} cells. 
Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
A non-toxic material which is suitable for the insulation is \gls{zro}. 
An economic and scalable method is doctor blading via a \gls{sg} process. 
\gls{sg} processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
\Gls{ml} can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance is performed with a particle swarm optimization 
algorithm. 
The resulting optimum is compared with other optimisation methods.

@@

The remainder of this work is organized with section 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background on topics of \gls{pv}, material science and computational science which were used in this work.
In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Gls{pv} is one viable option when becoming carbon neutral. 
Furthermore, 
it uses the suns energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of \gls{pv} are \gls{cigs}\cite{Vasekar2010} cells. 
Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any \gls{cigs} cells can be synthesised on top.
\td{Polymere would be a obvious choice if not for its low melting point.}
A non-toxic material which is suitable for the insulation is \gls{zro}. 
An economic and scalable method is doctor blading via a \gls{sg} process. 
\gls{sg} processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
\Gls{ml} can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance is performed with a particle swarm optimization 
algorithm. 
The resulting optimum is compared with other optimisation methods.

@@

The remainder of this work is organized with section 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background on topics of \gls{pv}, material science and computational science which were used in this work.
In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
Finally, section \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-02-27 Thesis/chapter/04-experimental.tex
formatting

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\section{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

\begin{table}[h]
	\centering
    \caption{Heating programs}
	\label{tab:heating}
    \subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
	\label{tab:labtech}
	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline
		\hline
		T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
		t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
		\hline
		\hline
	\end{tabular}
%%%%%%%%%%%%
    \subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
	\label{tab:nt}
	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline\hline
		Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
		\hline
		NT1		&2					&1					&2				&400	&60  \\
		NT2		&2					&2					&2				&400	&60  \\
		NT3		&3					&3					&3				&400	&60  \\
		NT4		&4					&4					&4				&400	&60  \\
		NT5		&4					&4					&4				&500	&60  \\
		NT6		&1					&1					&1				&400	&60  \\
%		NT7		&max				&max				&max			&600	&60  \\
		\hline\hline
	\end{tabular}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\section{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

\begin{table}[h]
	\centering
    \caption{Heating programs}
	\label{tab:heating}
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
		\label{tab:labtech}
		\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
			\hline
			\hline
			T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
			t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
			\hline
			\hline
		\end{tabular}
	\end{subtable}
%%%%%%%%%%%%
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
		\label{tab:nt}
		\resizebox{\textwidth}{!}{
		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
			\hline\hline
			Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
			\hline
			NT1		&2					&1					&2				&400	&60  \\
			NT2		&2					&2					&2				&400	&60  \\
			NT3		&3					&3					&3				&400	&60  \\
			NT4		&4					&4					&4				&400	&60  \\
			NT5		&4					&4					&4				&500	&60  \\
			NT6		&1					&1					&1				&400	&60  \\
	%		NT7		&max				&max				&max			&600	&60  \\
			\hline\hline
		\end{tabular}
	}
	\end{subtable}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

### 2023-02-27 Thesis/chapter/063-discussion.tex
formatting

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimisation 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimisation, modelling and data generation}
\label{sec:phase3}
During the optimisation the main problems were too many in- and output variables, reproducibility and regularisation. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimisation the input data were not regularized, %es wurde auf regularisation verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi

>>>>

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimisation 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimisation, modelling and data generation}
\label{sec:phase3}
During the optimisation the main problems were too many in- and output variables, reproducibility and regularisation. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimisation the input data were not regularized, %es wurde auf regularisation verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi
